---
title: "Statistics II - Problem Set 4"
output:
  md_document:
    variant: markdown_github
---

## Exercise 08

> In this problem we will do a simple econometric exercise using Mroz (1987) data on the wages of 428 working, married 
> women. Use ~~Stata~~ **R** to answer the following items. Please attach your code to the answer. 
> 
> (a) Run the regression $\text{lwage} = \beta_0 + \beta_1 \text{kidslt6} + \beta_2 \text{kidsge6} + u$, where $\text{lwage}$ is the logarithm of the wage, 
> \text{kidslt6} the number of children less than six and \text{kidsge6} the number of children at least six years of age. Test the hypothesis $H_0 : \beta_1 = 0, \beta_2 = 0$.


```{r, echo=TRUE}
mroz = haven::read_dta("mroz.dta")
short = lm(lwage ~ kidslt6 + kidsge6, data = mroz)
summary(short)
```

Observe que `F = 3.117`, com `p-valor = 0.04532`. Rejeitamos a hipótese nula ao nível de confiança de 95%.

> (b) Comment on the exogeneity of the regressors from the last item.

(...)

> (c) Now run the regression $\text{lwage} = \beta_0 + \beta_1 \text{kidslt6} + \beta_2 \text{kidsge6} + \beta_3 \text{age} + \beta_4 \text{educ} + \beta_5 \text{exper} + \beta_6 \text{expersq} + u$

```{r, echo=TRUE}
long = lm(lwage ~ kidslt6 + kidsge6 + age + educ + exper + expersq, data = mroz)

rhs = c(0, 0)
row1 = c(0, 1, 0, 0, 0, 0, 0)
row2 = c(0, 0, 1, 0, 0, 0, 0)
H = matrix(data = c(row1, row2), nrow = 2, byrow = TRUE)
car::linearHypothesis(long, H, rhs)
```

Agora temos `F = 0.3538`, com `p-valor = 0.7022`. Não podemos, portanto, rejeitar a hipótese nula.
