---
title: "Statistics II - Problem Set 4"
output: html_document
---

## Exercise 08

> In this problem we will do a simple econometric exercise using Mroz (1987) data on the wages of 428 working, married 
> women. Use ~~Stata~~ **R** to answer the following items. Please attach your code to the answer. 
> 
> (a) Run the regression $$\text{lwage} = \beta_0 + \beta_1 \text{kidslt6} + \beta_2 \text{kidsge6} + u$$, where $\text{lwage}$ is the logarithm of the wage, 
> \text{kidslt6} the number of children less than six and \text{kidsge6} the number of children at least six years of age. Test the hypothesis $H_0 : \beta_1 = 0, \beta_2 = 0$.


```{r, echo=TRUE}
mroz = haven::read_dta("mroz.dta")
summary(lm(lwage ~ kidslt6 + kidsge6, data = mroz))
```

Observe que `F = 3.117`, com `p-valor = 0.04532`. Rejeitamos a hipótese nula ao nível de confiança de 95%.

> (b) Comment on the exogeneity of the regressors from the last item.

No item anterior estamos "estimando" o efeito de ter filhos de até 18 anos (em duas variáveis separadas) no salário de mulheres casadas e empregadas. Contudo esta especificação de regressão ignora que o próprio salário influencia a decisão de ter filhos, de modo que $\text{kidslt6}$ e $\text{kidsge6}$ são variáveis endogenamente determinadas. 

> (c) Now run the regression $\text{lwage} = \beta_0 + \beta_1 \text{kidslt6} + \beta_2 \text{kidsge6} + \beta_3 \text{age} + \beta_4 \text{educ} + \beta_5 \text{exper} + \beta_6 \text{expersq} + u$ where the last three variables are the woman’s years of education, years of experience in the market and years of experience squared.
Test the hypothesis $H_0: \beta_1 = 0, \beta_2 = 0$.

```{r, echo=TRUE}
long = lm(lwage ~ kidslt6 + kidsge6 + age + educ + exper + expersq, data = mroz)
short = lm(lwage ~ age + educ + exper + expersq, data = mroz)
anova(short, long)
```

> (d) Compare the tests from items (a) and (c). Comment on potential problems with our inference.

No item (c) obtemos `F = 0.3538`, com `p-valor = 0.7022`. Não podemos, neste caso, rejeitar a hipótese nula, ao contrário do que acontece no item (a). Apesar de incluirmos mais variáveis relevantes no modelo e diminuir o potencial de viés no estimador das variáveis de interesse, ainda não contornamos o problema de endogeneidade apontado no item (b).

